---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# countMissing

<!-- badges: start -->
<!-- badges: end -->

Given a data frame `data` and a column `group`, `count_all_missing_by_group()` creates a new data frame with one row per level of `group`. The first column of the output data frame contains the levels of `group`, and the rest of the columns contain the number of missing values for all columns in `data` except `group`.

## Installation

You can install the development version of countMissing from [GitHub](https://github.com/) with:

``` {r}
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/countMissing")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(countMissing)
## countMissing relies on tidyverse
library(tidyverse)
## load the dataset for the following demo
library(palmerpenguins)
```

This example computes the number of missing values in the `airquality` dataset grouped by the `cyl` column. 

```{r} 
count_all_missing_by_group(airquality, Month)
```

This example has the same output as the last example, but shows off an alternative way of invoking the `count_all_missing_by_group()`: piping the dataset into the function. 

```{r} 
airquality |> count_all_missing_by_group(Month) 
```

The optional `.groups` argument allows us to keep the output grouped by the grouping column. See example below; notice how the output is a grouped tibble, rather than the ungrouped tibble output of the earlier examples. 

```{r} 
count_all_missing_by_group(airquality, Month, .groups = "keep")
```
